### 2022-06-28 README.Rmd
unit tests improved

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. Much of its functionality and syntax mimics the corresponding base R functions. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Additional functions are available for multiple testing for the analysis of experimental designs. Details of the testing procedures are given in [Kim et al. (2021)](https://arxiv.org/abs/2112.09206).

@@

## Usage
```{r eval = TRUE}
library(melt)
# one sample test for mean
fit1 <- el_mean(par = 0, x = rnorm(n = 100))
confint(fit1)

# linear regression
fit2 <- el_lm(formula = mpg ~ wt, data = mtcars)
summary(fit2)
confint(fit2)

# analysis of variance 
data("clothianidin")
fit3 <- el_lm(clo ~ -1 + trt, clothianidin)
summary(fit3)
confint(fit3)

>>>>

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. Much of its functionality and syntax mimics the corresponding base R functions. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Additional functions are available for multiple testing for the analysis of experimental designs. Details of the testing procedures are given in [Kim, MacEachern, and Peruggia (2021)](https://arxiv.org/abs/2112.09206).

@@

## Usage
```{r eval = TRUE}
library(melt)
# one sample test for mean
fit1 <- el_mean(rnorm(n = 100), par = 0)
confint(fit1)

# linear regression
fit2 <- el_lm(mpg ~ wt, data = mtcars)
summary(fit2)
confint(fit2)

# analysis of variance 
data("clothianidin")
fit3 <- el_lm(clo ~ -1 + trt, data = clothianidin)
summary(fit3)
confint(fit3)
